On the Galaxy Size--Halo Connection

### 2017-08-30 paper/galsize_paper.tex
Updated references to Meert15
Finished sketch of galaxy sample description

@@

@@

>>>>

%%%%%%%%  units  %%%%%%%%
\newcommand{\kpc}{{\rm kpc}}
\newcommand{\mpc}{{\rm Mpc}}

@@

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively. We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.

@@

We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
